---
title: "INT 322 Visualization and Reporting Class 3a"
author: "Michael Haseley"
date: "November 22, 2017"
output:
  ioslides_presentation:
    logo: stamford.png
  beamer_presentation: default
always_allow_html: yes
---

## Introduction

Leaflet is one of the most popular Javascript libraries for
creating interactive maps. The leaflet R package allows you
to create your own leaflet maps without needing to know any
Javascript!

### Installation

```r
install.packages("leaflet")
```

## Your First Map

Getting started with leaflet is easy. The `leaflet()`
function creates a map widget that you can store in a
variable so that you can modify the map later on. You can
add features to the map using the pipe operator (`%>%`) just
like in dplyr. The `addTiles()` function adds mapping data
from [Open Street Map](http://www.openstreetmap.org/).

```{r, eval=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map
```

## Your First Map

```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map
```

## Adding Markers

You can add markers to your map one at a time using the
`addMarkers()` function by specifying the longitude and
latitude. ([Here's](https://www.gps-coordinates.net/)
a tip if you tend to mix them up.) You can specify popup
text for when you click on the marker with the `popup` 
argument.

```{r, eval=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=13.734288, lng= 100.662247, 
             popup="Evil Lair!")
my_map
```

## Adding Markers

```{r, echo=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=13.734288, lng= 100.662247, 
             popup="Evil Lair!")
my_map
```

## Adding Many Markers

Adding one marker at a time is often not practical if you
want to display many markers. If you have a data frame with
columns `lat` and `lng` you can pipe that data frame into
`leaflet()` to add all the points at once.

```{r, eval=FALSE}
set.seed(2017-11-22)
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```

## Adding Many Markers

```{r, echo=FALSE}
set.seed(2017-11-22)
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```

## Making Custom Markers

The blue markers that leaflet comes packaged with may not be
enough depending on what you're mapping. Thankfully you can
make your own markers from `.png` files.

```{r, eval=FALSE}
elIcon <- makeIcon(
  #iconUrl = "https://app.box.com/s/c00h7fey8k5ctst71sr3toj29v08dmrl",
  iconUrl = "el.png",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

poiLatLong <- data.frame(
  lat = c(13.734288, 13.7428346, 13.7497333),
  lng = c(100.662247, 100.5492751, 100.5409428))

poiLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = elIcon)
```

## Making Custom Markers

```{r, echo=FALSE}
elIcon <- makeIcon(
  #iconUrl = "https://app.box.com/s/c00h7fey8k5ctst71sr3toj29v08dmrl",
  iconUrl = "el.png",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

poiLatLong <- data.frame(
  lat = c(13.734288, 13.7428346, 13.7497333),
  lng = c(100.662247, 100.5492751, 100.5409428))

poiLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = elIcon)
```

## Adding Multiple Popups

When adding multiple markers to a map, you may want to add
popups for each marker. You can specify a string of plain
text for each popup, or you can provide HTML which will be
rendered inside of each popup.

```{r, eval=FALSE}
poiSites <- c(
  "<a href='http://www.deadmistress.com/'>The Dead Mistress</a>",
  "<a href='https://http://www.novotelbangkokploenchit.com/'>NOVOTEL BANGKOK PLOENCHIT SUKHUMVIT</a>",
  "<a href='http://http://novotelbangkokplatinum.com//'>NOVOTEL BANGKOK PLATINUM PRATUNAM</a>"
)

poiLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = elIcon, popup = poiSites)
```

## Adding Multiple Popups

```{r, echo=FALSE}
poiSites <- c(
  "<a href='http://www.deadmistress.com/'>The Dead Mistress</a>",
  "<a href='https://http://www.novotelbangkokploenchit.com/'>NOVOTEL BANGKOK PLOENCHIT SUKHUMVIT</a>",
  "<a href='http://http://novotelbangkokplatinum.com//'>NOVOTEL BANGKOK PLATINUM PRATUNAM</a>"
)

poiLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = elIcon, popup = poiSites)
```

## Mapping Clusters

Sometimes you might have so many points on a map that it
doesn't make sense to plot every marker. In these situations
leaflet allows you to plot clusters of markers using
`addMarkers(clusterOptions = markerClusterOptions())`. When
you zoom in to each cluster, the clusters will separate until
you can see the individual markers.

```{r, eval=FALSE}
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```

## Mapping Clusters

```{r, echo=FALSE}
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```

## Mapping Circle Markers

Instead of adding markers or clusters you can easily add
circle markers using `addCircleMarkers()`.

```{r, eval=FALSE}
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers()
```

## Mapping Circle Markers

```{r, echo=FALSE}
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers()
```

## Drawing Circles

You can draw arbitrary shapes on the maps you create,
including circles and squares. The code below draws a map
where the circle on each city is proportional to the
population of that city.

```{r, eval=FALSE}
md_districts <- data.frame(name = c("Prawet", "Suan Luang", "Saphan Sung"),
                        pop = c(172761, 121740, 98854),
                        lat = c(13.7156255, 13.7354311, 13.7676357),
                        lng = c(100.69589240000005, 100.64082350000001, 100.69288040000004))
md_districts %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_districts$pop) * 30)
```

## Drawing Circles

```{r, echo=FALSE}
md_districts <- data.frame(name = c("Prawet", "Suan Luang", "Saphan Sung"),
                        pop = c(172761, 121740, 98854),
                        lat = c(13.7156255, 13.7354311, 13.7676357),
                        lng = c(100.69589240000005, 100.64082350000001, 100.69288040000004))
md_districts %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_districts$pop) * 30)
```

## Drawing Rectangles

You can add rectangles on leaflet maps as well:

```{r, eval=FALSE}
leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 13.734174107359014, lng1 = 100.66013932228088, 
                lat2 = 13.736341888685688, lng2 = 100.66200613975525)
```

## Drawing Rectangles

```{r, echo=FALSE}
leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 13.734174107359014, lng1 = 100.66013932228088, 
                lat2 = 13.736341888685688, lng2 = 100.66200613975525)
```

## Adding Legends

Adding a legend can be useful if you have markers on your
map with different colors:

```{r, eval=FALSE}
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```

## Adding Legends

```{r, echo=FALSE, message=FALSE}
df <- data.frame(lat = runif(20, min = 13.6, max = 13.8),
                 lng = runif(20, min = 100.5, max = 100.7),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```

## Conclusion

For more details about the leaflet package for R 
visit http://rstudio.github.io/leaflet/.
