---
title: "My Fancy Presentation"
author: "Michael Haseley"
date: "November 29, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## My New Slide
Content
Content

***
No title Slide

## My Title

### A top level subheading

#### A second level subheading
 
- Bullet one
- Bullet two

1. Item A
2. Item B

## Basic Formatting

Plain text!

*italicized text*

**Bold Text**

`for (i %in% 1:10)`

## Running Code

```{r}
head(mtcars)

```
## Running code Remove Comments

```{r, comment = ""}
head(mtcars)

```

## Running Code no comments with echo

```{r, comment = "", echo=TRUE}
head(mtcars)

```
You could also change these options below the YAML and format the entire document

## Display Code no execution

```{r, comment = "", echo=TRUE, eval=FALSE}
head(mtcars)

```

## Slide with Plot

```{r echo=FALSE, fig.align='center', fig.cap="My Awesome Caption"}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```

